Understanding Vulnerability: Toronto Police Service's Annual Statistical Report on Crimes Against the Person(2014-2022)

### 2024-01-23 output/paper/paper.qmd
quarto file to render pdf

---
title: "UntitledUnderstanding Vulnerability: Toronto Police Service's Annual Statistical Report on Crimes Against the Person (2014-2022)"
author: "Jagpreet Singh"
format: pdf
editor: visual
---

```{r}
knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
```
```{r}
#| lable: Table 1

@@

#| label - Fig-1

@@

#| label: fig-2

@@

# Create a bar graph using ggplot2 with subtype on the bars
ggplot(subtype_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, fill = SUBTYPE)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  labs(title = "Total count of crimes against the person per year by type of crime (2014-2022)",
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(subtype_counts$COUNT_), by = 2000)) +
  theme_minimal()
```

#| label: fig-3

@@

```
```{r}

@@

# Create a line graph using ggplot2 with age_group on the x-axis
ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_GROUP, group = AGE_GROUP)) +
  geom_line(size = 1, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7) +
  labs(title = "Total count of crimes against the person of each age group per year",
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(age_counts$COUNT_), by = 2000)) +
  scale_color_manual(values = c("Youth" = "blue", "Child" = "red", "Adult" = "green", "Unknown" = "purple"),
                     labels = c("Youth" = "Youth", "Child" = "Child", "Adult" = "Adult", "Unknown" = "Unknown")) +  # Specify colors and labels
  theme_minimal()

```
```{r}
#| label: Table-2

@@

# Print the resulting table
print(result_table)
```

>>>>

---
title: "Understanding Vulnerability: Toronto Police Service's Annual Statistical Report on Crimes Against the Person(2014-2022)"
author: "Jagpreet Singh"
format: pdf
editor: visual
Abstract:
---

```{r}
knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
```

## Introduction

## Data

```{r}
#| lable: Table 1

@@

```{r}
#| label: Fig-1

@@

```{r}
#| label: fig-2

@@

# Create a bar graph using ggplot2 with subtype on the bars
ggplot(subtype_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, fill = SUBTYPE)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  labs(title = "Total count of crimes against the person per year by type of crime (2014-2022)",
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(subtype_counts$COUNT_), by = 2000)) +
  theme_minimal()

```{r}
#| label: fig-3

@@

@@

# Create a line graph using ggplot2 with age_group on the x-axis
ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_GROUP, group = AGE_GROUP)) +
  geom_line(linewidth = 1, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7) +
  labs(title = "Total count of crimes against the person of each age group per year",
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(age_counts$COUNT_), by = 2000)) +
  scale_color_manual(values = c("Youth" = "blue", "Child" = "red", "Adult" = "green", "Unknown" = "purple"),
                     labels = c("Youth" = "Youth", "Child" = "Child", "Adult" = "Adult", "Unknown" = "Unknown")) +  # Specify colors and labels
  theme_minimal()

```{r}
#| label: Table-2

@@

# Print the resulting table
print(result_table)
